An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
remove commented properteis of significance

We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$.
We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ x_\text{bound}= 1  / \tan(\alpha_\text{max} / 2)$.
Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
The significant portion is given by $ x_\text{bound} = 1  / 2 \tan(\alpha_\text{max} / 2)$
These specific cases can easily be transformed into all possible cases using scaling and rotation operations.

@@

\iffalse

\subsubsection{Properties of significant regions}
%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
See \cref{distance_ratio_limit}.
The condition $|v - p| = \Delta R$ is true exactly for those ST edges between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked edges, so we can perform the trapezoidation after marking.

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the ST can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore not significant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

\begin{lemma}\label{saddle_points_are_marked}
A saddle point is always marked, i.e.\
when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
\end{lemma}
\begin{proof}
You will either go through the marked region of a discretized parabola or of an edge with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
\end{proof}

\begin{lemma}\label{single_upward_edge}
From any node in the ST which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Edges added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
\end{proof}

\fi

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
The two downward edges from a branch point cannot both be significant.
A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
This means that all support points lie within a \SI{180}{\degree} range around the node. 
Suppose the one edge going upward is generated by $p_1$ and $p_3$.
Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.
\fi

%\subsubsection{Marking filtering}
\paragraph{Marking filtering}
After initializing all marked edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.

>>>>

We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$ and $R(x) = y(x)$.
We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ | x_\text{bound} | = (\tan(\alpha_\text{max} / 2))^{-1}$.
Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
The boundaries of significance are given by $ | x_\text{bound} | = \nicefrac12 (\tan(\alpha_\text{max} / 2))^{-1}$.
From these we can derive the locations $l = (\pm x_\text{bound}, y(x_\text{bound}))$.
These specific cases can easily be transformed into all possible cases using scaling and rotation operations.

@@

%\subsubsection{Marking filtering}
\paragraph{Marking filtering}
After initializing the marking at all edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
